What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-26 android-stacks.tex
More improvements on introduction

Along the recent years, we have witnessed an astonishing increase in the number 
mobile applications available. Such increase is motivated by pervasiveness of the World Wide Web 
and the unprecedent increase of global smartphone shipments -
the mobile industry shiped over 315 million smartphones in the last quarter of 2013 [ref-IO].

@@

In this context, Android is currently the leading plaftorm of such applictions - thanks to its open-source 
model and hardware partners like Samsung, HTC, Motorola, Asus (besides Nexus its
 own device) [ref].  Google estimates that there is over 1 billion Android active users per month [ref-IO],
and the number of apps built on top of Android increases in a daily rate.

@@

If on the one hand such applications extend the phones capabilities 
far beyond of the basic calls and textual messages, on the other hand
they have to face to new challenges imposed by mobile environmet.
Such applications have to cope with an increasing number of abnormal
computation states, arising from: programmming errors;
 noisy user inputs; faults in underlying middleware or hardware; 
faults on third party services and libraries, compatibility issues [ref], 
conection with devices e.g., as GPS, camera, memory and batery restrictions
among others.

@@

In the same rathe the number of number of mobile appsincreases, also increases 
the number of users affected by their failures. Our conjecture is that several 
Android applicatons may be suffering from similar vulnerabilities on the exception 
handling code of the applications themselves or on the underlaying platform, and 
that such vulnerabiliries may be leading to application crashes.

Untill recent years, the availability of issues reporting abnormal
computation states (e.g., crashes) was scarce. The
available data comprised few large scale projects (e.g. the Mozilla
crash report dataset\footnote{https://code.google.com/p/promisedata/issues/detail?id=88}).
Recently we have observed a rapid increase in the number of open
source projects that make their control version and issue tracking systems
publicly available in repository hosting sites such as GitHub and Googlecode.

@@

Previous studies on crash report analysis focused a system 
at a time. Moreover, none of them target a family of Android applications (which share a common core) extracting 
the characteristics on exceptional issues and looking for similar vulnerabilities on applications and underlaying platform.

@@

\begin{table*}
  \centering
  \begin{tabular}{llcccccc}
    \hline
    \bfseries{Wrapper Type}  &  \bfseries{Root Cause Type} &  \bfseries{Projects}  &  \bfseries{Occurrences} & \textsf{Android} & \textsf{Libcore} & \textsf{App} & \textsf{Lib}  \\
    \hline
      Runtime &  Checked   & 70 & 114 & 0 &  0  & 0 &  0 \\
      Runtime   &  Error   & 38  & 57 & 0 &  0  & 0 &  0 \\
      Checked &  Runtime   & 12 & 22 & 0 &  0  & 0 &  0 \\
      Checked & Error      & 7 &  8 & 0 &  0  & 0 &  0 \\
      Error & Checked      & 4  &  7 & 0 &  0  & 0 &  0     \\
      Error & Runtime     & 6  &  13   & 0 &  0  & 0 &  0    \\
     Throwable & Runtime   & 1 &  3   & 0 &  0  & 0 &  0    \\
    \hline
  \end{tabular}
\caption{Wrappings comprising different exception types.}
\label{tab:wrappingandroid}
\end{table*}

>>>>

Along the recent years, we have witnessed an astonishing increase in the number 
mobile applications publicly available. Such increase is motivated by pervasiveness of the World Wide Web 
and the unprecedent increase of global smartphone shipments -
the mobile industry shiped over 315 million smartphones in the last quarter of 2013 [ref-IO].

@@

In this context, Android has become the leading plaftorm of such applictions - thanks to its open-source 
model and hardware partners like Samsung, HTC, Motorola, Asus (besides Nexus its
 own device) [ref].  Google estimates that there is over 1 billion Android active users per month [ref-IO],
and the number of apps built on top of Android increases in a daily rate.

@@

If on the one hand such applications extend the phones capabilities 
far beyond of the basic calls and textual messages, on the other hand
they have to cope to new challenges imposed by mobile environmet.
Such applications have to cope with an increasing number of abnormal
computation states, arising from: programmming errors;
 noisy user inputs; faults in underlying middleware or hardware; 
faults on third party services and libraries, compatibility issues [ref], 
conection with devices e.g., as GPS, camera, memory and batery restrictions
among others.

@@

Google estimates that Android has over 1 billion active users per month, 
who pull out theirs phones and check it over 100 bilion times. 
In the same rate the number of mobile users increase, also increases 
the number of users affected by faulty apps and app crashes.

%If we google for "Android app crashes"
% we can find 1.200.000 pages about the subject on forums and blogs. In Feb. 2014
%Gartner issue a report on mobile technologies and capabilities 
%[ref-https://www.gartner.com/doc/2665315/top--mobile-technologies-capabilities], 
%which emphasized the importance of monitoring application crashes.

Our conjecture is that several Android applicatons may be suffering from similar 
vulnerabilities on the exception handling code of the applications themselves or 
on the underlaying platform, and that such vulnerabiliries may be leading to
 application crashes -  as Uncaught Exceptions lead to app to crashes in
Android and is one of the main causes of application crashes in Java [ref AST] .

Untill recent years, the availability of issues reporting abnormal
computation states (e.g., crashes) was scarce. The
available data comprised only few large scale projects (e.g. the Mozilla
crash report dataset\footnote{https://code.google.com/p/promisedata/issues/detail?id=88}).
Recently we have observed a rapid increase in the number of open
source projects that make their control version as well as the issue tracking systems
publicly available in repository hosting sites such as GitHub and Googlecode.

@@

Most of such studies, however, focused the analysis on one or two system at a time. None 
of them target crash-related information of family of Android applications 
(which share a common core) aiming at  extracting their common characteristics 
 and looking for similar vulnerabilities on applications and underlaying platform.

@@

\begin{table*}
  \centering
  \begin{tabular}{llcccccc}
    \hline
    \bfseries{Wrapper Type}  &  \bfseries{Root Cause Type} &  \bfseries{Projects}  &  \bfseries{Occurrences} & \textsf{Android} & \textsf{Java/Libcore} & \textsf{Lib} & \textsf{App}  \\
    \hline
      Runtime &  Checked   & 70 & 114 & 66 &  0  & 19 &  29 \\
      Runtime   &  Error   & 38  & 57 & 50 &  0  & 6 &  1 \\
      Checked &  Runtime   & 12 & 22 & 4 &  0  & 9 &  9 \\
      Checked & Error      & 7 &  8 & 5 &  0  & 0 &  3 \\
      Error & Checked      & 4  &  7 &  &  0  & 7 &  0     \\
      Error & Runtime     & 6  &  13   & 1 &  1  & 0 &  11    \\
    \hline
  \end{tabular}
\caption{Wrappings comprising different exception types.}
\label{tab:wrappingandroid}
\end{table*}
